%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
        {Rong Lu Lab, Keck School of Medicine, Stem Cell and Regenerative Medicine, USC} % Job title
        {Research Assistant} % Organization
        {Los Angeles, CA} % Location
        {Aug. 2019 - present} % Date(s)
        {
        \begin{cvitems} % Project and achievement
                % Aging
                \vspace{0.5em}
                \item[] \hspace{-1em}{\textbf{Investigating aging-related physiological decline in hematopoiesis}}
                \vspace{0.5em}
                \item {Identified Hematopoietic Stem cells (HSCs) that are early and delayed aging;}
                \item {Found distinct regulators of hematopoiesis are associated with early and delayed aging  ;}
                \item {Tracked and analyzed individual HSC clones in early and delayed aging mice.}
                % Aging
                \vspace{0.5em}
                \item[] \hspace{-1em}{\textbf{Investigating heterogeneous response to the leukemic mutations}}
                \vspace{0.5em}
                \item {Identified clonal over-expansion in \textit{Tet2} knock-out mice;}
                \item {Characterized clonal differentiation bias in control and \textit{Tet2} knock-out mice;}
                \item {Found differential gene expression changes are associated with clonal expanding.}
                % ALL
                \vspace{0.5em}
                \item[] \hspace{-1em}{\textbf{Studying intratumoral heterogeneity using clonal tracking technology and xenograft mouse model}}
                \vspace{0.5em}
                \item {Identified distinct leukemia clones expanding in extramedullary organs;}
                \iterm {Characterized clonal selection during serial transplantation.}
         \end{cvitems}
        }
    % Rong lab
    \cventry
        {Rong Lu Lab, Keck School of Medicine, Stem Cell and Regenerative Medicine, USC} % Job title
        {Research Technician} % Organization
        {Los Angeles, CA} % Location
        {Sept. 2018 - July 2019} % Date(s)
        {
            \begin{cvitems} % Project and achievement
                \vspace{0.5em}
                \item {Data analysis for clonal hematopoietic compensation;}
                \item {Optimized data analysis algorithm for clonal tracking technology.}
                \vspace{0.5em}
            \end{cvitems}
        }
   % Fang lab     
    \cventry
        {Jianmin Fang Lab, School of Life Science and Medicine, Tongji University} % Job title
        {Graduation thesis} % Organization
        {Shanghai, China} % Location
        {Sept. 2015 - July 2016} % Date(s)
        {
            \begin{cvitems} % Project and achievement
                \vspace{0.5em}
                \item[] \hspace{-1em}{\textbf{Mechanism of \textit{IL11/STAT3} Signal Pathway on Lewis Lung Carcinoma(LLC)}}
                \item {Established the IL-11 over-expression model to functionally verify IL-11 promote resistance of LLC to VEGF-Trap.}
                \vspace{0.5em}
            \end{cvitems}
        }    
\end{cventries}
